### 2020-06-19 Strings2020/strings6/strings6.tex
Add strings6 & update advqft2
... about FP quantization

	The $D = d+1$ dimensional metric can be parameterized as follows:
	\begin{gather}
		\dd{s}^2
		= G_{MN}^D \dd{x^M} \dd{x^N}
		= G_{\mu\nu} \dd{x^\mu} \dd{x^\nu}
			+ e^{2\sigma}\,\pqty{
				\dd{x^d} + A_\mu \dd{x^\mu}
			}^2,
	\\
		G^D_{\mu\nu}
		= G_{\mu\nu} + e^{2\sigma} A_\mu A_\nu,\quad
		x^d \cong x^d + 2\pi R
	\end{gather}
	Where $\mu = 0,1,\cdots,(d-1)$ labels the noncompact directions, and the $x^d$ direction is compactified. $G_{\mu\nu},\sigma$ and $A_\mu$ should depend only on the noncompact coordinates $x^\mu$, $A^\mu = G^{\mu\nu} A_\nu$.

@@

	\item The above mechanism provides a natural theory of gravity and electromagnetism in $d = 4$. Note that the gravitational and gauge couplings are related with the radius of the compact dimension:
	\begin{equation}
		\frac{g_d^2}{\kappa_d^2}
		= \frac{2}{\rho_0^2}
	\end{equation}
	In reality gravity is much weaker than electromagnetism, which means that $\rho_0 \to 0$, or $R\to 0$ if we gauge-fix $\sigma_0 \equiv 0$. In other words, the radius is constrained by the ratio of the couplings:
	\begin{equation}
		R \sim \sqrt{2}\,\frac{\kappa_d}{g_d}
	\end{equation}
	\end{enumerate}

>>>>

	The $D = d+1$ dimensional metric can be parameterized as follows:
	\begin{gather}
		\dd{s}^2
		= G_{MN}^D \dd{x^M} \dd{x^N}
		= G_{\mu\nu} \dd{x^\mu} \dd{x^\nu}
			+ e^{2\sigma}\,\pqty{
				\dd{x^d} + A_\mu \dd{x^\mu}
			}^2,
	\label{eq:metric_decomp}
	\\
		G^D_{\mu\nu}
		= G_{\mu\nu} + e^{2\sigma} A_\mu A_\nu,\quad
		x^d \cong x^d + 2\pi R
	\label{eq:sub_metric_convention}
	\end{gather}
	Where $\mu = 0,1,\cdots,(d-1)$ labels the noncompact directions, and the $x^d$ direction is compactified. $G_{\mu\nu},\sigma$ and $A_\mu$ should depend only on the noncompact coordinates $x^\mu$, $A^\mu = G^{\mu\nu} A_\nu$.

@@

	\item The above mechanism provides a natural theory of gravity and electromagnetism in $d = 4$. Note that the gravitational and gauge couplings are related with the radius of the compact dimension:
	\begin{equation}
		\frac{g_d^2}{\kappa_d^2}
		= \frac{2}{\rho_0^2}
	\end{equation}
	In reality gravity is much weaker than electromagnetism, which means that $\rho_0 \to 0$, or $R\to 0$ if we gauge-fix $\sigma_0 \equiv 0$. In other words, the radius is constrained by the ratio of the couplings:
	\begin{equation}
		R \sim \sqrt{2}\,\frac{\kappa_d}{g_d}
	\end{equation}

	\item \textbf{Fiberwise T-Duality and the Dilaton}
	\begin{enumerate}
	\item For a bosonic string moving in a general background of massless fields in $D = d + 1 = 26$, its worldsheet action is given by:
	\begin{equation}
		S = \frac{1}{4\pi\alpha'}
			\int \dd[2]{\sigma} \sqrt{g}\,
			\Bqty\Big{
				\pqty{
					g^{ab} G_{MN}(X)
					+ i\epsilon^{ab} B_{MN}(X)
				}\,
				\pdd{a} X^M
				\pdd{b} X^N
				+ \alpha'\mcal{R}\,\Phi(X)
			}
	\end{equation}
	Where $\Phi$ is the worldsheet Ricci scalar. The $X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.

	$G_{MN}$ can be further split into $G_{\mu\nu},G_{\mu d}$ and $G_{dd}$ with $d = 25$, in a way similar to \eqref{eq:metric_decomp}, but here we are using a simpler convention, with $G^D_{\mu\nu} = G_{\mu\nu}$ instead of \eqref{eq:sub_metric_convention}. Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetricity.

	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxilary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
	\begin{equation}
	\small
	\begin{aligned}
		\mcal{L}_d[X^d,A_a]
		&= \frac{\sqrt{g}}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					g^{ab} G_{\mu d}
					+ i\epsilon^{ab} B_{\mu d}
				}
					\,(\pdd{a} X^d + A_a)\,
					\pdd{b} X^\mu
				+ g^{ab} G_{dd}
					\,(\pdd{a} X^d + A_a)\,
					\,(\pdd{b} X^d + A_b)
			} \\
	\end{aligned}
	\end{equation}

	Consider a translation $
		X^d\mapsto X^d + \lambda
	$, where $\lambda$ depends on $X^\mu = X^\mu(\sigma)$ and hence depends on the worldsheet coordinates $\sigma$; it is clear that:
	\begin{gather}
		\pdd{a} \pqty{X^d + \lambda}
			+ \pqty{A_a - \pdd{a}\lambda}
		= \pdd{a} X^d + A_a,
	\quad
		\mcal{L}_d \bqty{
			\pqty{X^d + \lambda},
			\pqty{A_a - \pdd{a}\lambda}
		}
		= \mcal{L}_d\bqty{
			X^d, A_a
		}
	\end{gather}
	i.e.\ $X^d$ translation is equivalent to a local gauge transformation $A_a\mapsto A_a - \pdd{a}\lambda$.

	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxilary field $\phi(\sigma)$ and an extra term:
	\begin{equation}
		\mcal{L}_d
		\longmapsto \mcal{L}_d
			+ i\epsilon^{ab} F_{ab}\,\phi,
	\quad
		F_{ab}
		= \pdd{a} A_b - \pdd{b} A_a,
	\quad
		\int \DD{\phi}\,
			e^{-i\epsilon^{ab} F_{ab}\,\phi}
		\sim \delta\bqty{
				\epsilon^{ab} F_{ab}
			}
	\end{equation}
	Which forces $F_{12} \equiv 0$ in the remaining path integral. Note that the only non-zero independent component of $F_{ab}$ in 2D is $F_{12}$, therefore $F_{12} \equiv 0$ implies that $F_{ab} \equiv 0$, or $
		F = \dd{A} = 0
	$. On the plane, this implies that $A = \dd{\lambda}$, i.e.\ it is indeed pure gauge\footnote{
		However, if there are punctures on the worldsheet, then there is non-trivial cohomology, and $A$ need not be $\dd{\lambda}$. I have not yet understood how this would affect our result; this problem is also acknowledged in \textit{Blumenhagen et al}, Chapter 14, yet it seems to simply ignore such issue. 
	}.

%	\begin{equation}
%		\int \DD{X}\,\DD{A_a}\,\DD{\phi}\,
%			e^{-S'}
%	\end{equation}

	We can then proceed to integrate out $A_a$. Since $A = \dd{\lambda}$, we can gauge fix $A \equiv 0$, and the action reduces to the original one:
	\begin{equation}
		S'\bqty{X,\phi=0,A_a=0}
		= S\bqty{X}
	\end{equation}
	Following the Faddeev--Popov procedure, we find that the path integral also reduces to the original one, up to some additional gauge volume determinant $\Delta_{FP}$, which is independent of $X$. This implies that the theory for the fields $(X,\phi,A_a)$ is, indeed, equivalent to that of the original string theory which has only the $X$ fields.

	\item Following our discussions in (b), we see that:
	\begin{equation}
		\pdd{a} X^d + A_a
		= 0 + A_a - \pdd{a} \lambda,\quad
		\lambda = -\pdd{a} X^d,
%	\\
%		\int \DD{X^d}\,
%			e^{-S'[X,\phi,A]}
%		= \int \DD{\lambda}\,
%			e^{-S'[X^d\equiv 0,\phi,A_\lambda]},\quad
%		A_\lambda = A - \dd{\lambda},
	\end{equation}
%	i.e.\ integrating over $X^d$ is equivalent to integrating over all the gauge configurations of $A$, labeled by $\lambda$, but with $X^d \equiv 0$. 
	Before completing the path integral, we perform a gauge transformation $
		A_a \mapsto A_a - \pdd{a} \lambda
	$, with $\lambda =  -X^d$. Assuming that there is no anomaly, we can ignore the functional Jacobian of the transformation, and the path integral shall be gauge invariant; in this case, the $\pdd{a} X^d$ term is canceled precisely by the gauge transformation, which is equivalent to setting $X^d = 0$ in the action:
	\begin{equation}
		S''\bqty{
				X^\mu,\phi,A
			}
		= S'\bqty{
				X^\mu,X^d = 0,\phi,A
			}
	\end{equation}
